Type Refinements for the Working Class

### 2015-12-24 paper.tex
remove remark; improve wording

On the other hand, (the analogues of) these theorems are \emph{not} valid under
Allen's supervaluation semantics, because one would have to account for worlds
at which an infinite number of atoms have already been generated; in this way,
the open-endedness of Allen's semantics relies crucially on a condition that is
simply impossible under a Brouwerian conception of mathematical activity.

\begin{remark}
  One way to recover something essentially equivalent to the supervaluation
  semantics in our style would be to replace the current semantic universe
  $\Define{\SemU}{\Classes^\SCtx}$ with an extended universe
  $\Define{\SemU_\infty}{\Classes^{\SCtx_\infty}}$, $\SCtx_\infty$ the set of
  possibly-infinite symbol contexts and injective, sort-preserving renamings.
  Externally, by Theorem~\ref{thm:no-nat-injection} we could still never
  exhibit an embedding of the naturals, but internally, we would be unable to
  rule it out.
\end{remark}

>>>>

On the other hand, (the analogues of) these theorems are \emph{not} valid under
Allen's supervaluation semantics, because one would have to account for worlds
at which an infinite number of atoms had already been generated; in this way,
the open-endedness of Allen's semantics relies crucially on a condition that is
simply impossible under a Brouwerian conception of mathematical activity.
